### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically. The proposed method can produce the conservative estimation of the side-channel leakage of the deterministic program. As a result, any severe leakage reported by \ctool{} is the true severe leakage. We also study the total effect of two leakages. Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

>>>>

In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically. The proposed method can produce the conservative estimation of the side-channel leakage of the deterministic program. As a result, any severe leakage reported by \ctool{} is the true severe leakage. We also study the total effect of two leakages. Using statistical hypothesis testing, we are able to determine if the two leakages are independent. If so, we can calculate the sum of the amount of leakage by adding two leakages. Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

In conclusion, this dissertation research develops practical techniques for side-channels in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We also open source the tool in the dissertation to facilitate the future research in the area.

In the future, we plan to explore the following directions based on the dissertation research.

\textbf{Kernel Space Side-channel Vulnerability Detection.}
